### 2016-11-16 conclusion.tex
Slight conclusion tweaks

Chapter 4 took these results to the limit to examine whether SN alone are able
to regulate the formation of stars in galaxies both heavier and lighter than the
Milky Way.  By simulating and examining a new sample of 18 galaxies (the
McMaster Unbiased Galaxy Simulations 2), we were able to demonstrate a critical
mass at which SN feedback breaks down as a regulator of gas accretion and star
formation.  Galaxies that exceed this mass, $(\sim 10^{12}\;\Msun)$, will produce
more stars than real galaxies, and produce much of these stars in a dense
stellar bulge.  All of this arises due to a fundamental relation between the
mass loading of superbubble driven winds and the mass of the galaxy (either its
halo or its disc).  When the escape velocity of the disc exceeds the sound speed
of superbubble-heated gas (which has a typical mass loading of $\eta=10$), only
outflows which have entrained less material are able to escape the galaxy,
leading to decreasing efficiency in ejecting material, and a shutdown of
SN regulation.  The fact that this shutdown occurs exactly where powerful AGN
are observed, and that it results in a vigorous transport of gas to the nucleus
of the galaxy make this result strong evidence that this shutdown acts as a kind
of ``hand-off'' between SN and AGN feedback.

@@

\section{Results in Context}
Developing a versatile, accurate, resolution insensitve model for feedback has
been a challenge in galaxy simulations for decades.  While a number of recent
models have been developed that are able to produce galaxies which match some
observables, all of these models have relied on purely numerical features to
enhance the effectiveness of feedback and counter the effects of limited
resolution.  The \citet{Keller2014} presented in Chapter 2 is the first model of
its kind that uses a first-principles approach to prevent overcooling.  Beyond
merely ``sufficient'' feedback, the superbubble model also incorporates physics
that previously have been omitted.  Thermal evaporation is a key process for
mixing cold ISM with hot feedback ejecta.  Prior to \citet{Keller2014}, this
process was completely ignored, and the local mass-loading of feedback was set
purely as a numerical parameter.  \citet{Rosdahl2016} illustrated this clearly,
in a recent comparison project.  This paper implemented 5 popular feedback
algorithms (simple thermal dumps; a delayed cooling model similar to
\citet{Agertz2013}; a kinetic model similar to \citet{DallaVecchia2008}; a
stochastic thermal model based on \citet{DallaVecchia2012}; and a hybrid model
from \citet{Kimm2015}) in the {\sc RAMSES} code.  This allowed for a controlled
test with isolated dwarf and Milky Way analog galaxies. Each of these models,
with ``fiducial'' parameter choices, produced star formation rates that varied
by nearly an order of magnitude in the \citet{Kennicutt1998} star formation
relation.  On top of that, the galaxies showed marked morphological differences
and average wind mass loadings that varied by nearly 4 orders of magnitude.  As
we showed in \citet{Keller2015}, these winds are critical to the formation of
galaxies like the Milky Way.  On top of the inter-model variation,
\citet{Rosdahl2016} also found that the numerical free parameters for each model
had a vast impact on the resulting galaxy star formation rate, morphology, and
outflow properties.  By building a more conservative, physically motivated
model where the local mass loading of supernovae feedback is set by thermal
evaporation, rather than numerically, we can sidestep many of these issues.

The issue of local mass loading has been explored before in simulation.
\citet{Thacker2000} showed a survey of methods for depositing feedback energy.
This work showed that choosing to deposit feedback energy into single resolution
elements vs. smoothing it over an SPH kernel had a significant impact on whether
that feedback energy could couple to the ISM.  \citet{Thacker2000} advocated the
use of a brief adiabatic period, similar to the delayed cooling model presented
in \citet{Rosdahl2016} to prevent overcooling when feedback energy was smoothed.
A more recent study by \citet{DallaVecchia2012} directly looked at the question
of local mass loading with a model that allowed the temperature of post-feedback
gas to be a single tunable parameter.  This is effectively the same as choosing
the amount of mass that each supernovae couples to.  They found that lower mass
loadings result in hotter post-feedback gas, with longer cooling times, and
subsequently much more effective supernovae feedback.  The \citet{Keller2014}
superbubble model is the first model to actually incorporate a physical
mechanism for determining this mechanism.  Previous feedback models have been
designed primarily to avoid the overcooling that can occur when this mass
loading is too high: superbubble feedback instead attempts to calculate the {\it
correct} local mass loadings, and allows the feedback-heated gas to cool with
realistic temperatures and densities.  By building a more physically motivated
model for supernovae feedback, we can have better confidence that results in
simulations testing the effects of this feedback arise from physics rather than
numerics.

As we showed in \citet{Keller2015}, including thermal evaporation in simulations
of a Milky Way like galaxy will drastically change the effectiveness of
SN-driven galactic winds.  Removing gas from the galaxy is the only effective
mechanism for regulating star formation on cosmic timescales.  To prevent the
formation of bulges larger than the ones seen in the local universe, bulge
forming gas (low-angular momentum gas) must be removed from the ISM; because
SN-driven winds are most effective at high redshift, when this material is
mostly accreted, the outflows driven from the galaxy preferentially remove
bulge-forming gas.  A similar result was seen in simulations of dwarf galaxies
by \citet{Brook2011}, but \citet{Keller2015} is the first work to show that
bulgeless disc galaxies similar in mass to the Milky Way can be produced through
the same mechanism, and connect this with the regulation of star formation.  An
important conclusion of this study is that much of the past work
\citet{Stinson2013,Agertz2013,Hopkins2014} showing that SN feedback was unable
regulate star formation without the addition of ``early feedback'' from
radiation pressure, stellar winds, or photoionization was likely underestimating
the effectiveness of SN.  Since many of these studies used simpler, more
numerically-sensitive feedback models that also omitted thermal evaporation,
they were unable to effectively drive the correct amount of mass into hot, high
entropy gas that could leave the galaxy.  This study tells us that the
disc-dominant morphology and low stellar fraction in galaxies like our own all
arise from the same mechanism:  heavily mass loaded, high redshift
winds.

>>>>

Chapter 4 took these results to the limit to examine whether SN alone are able
to regulate the formation of stars in galaxies both heavier and lighter than the
Milky Way.  By creating a new sample of 18 simulated galaxies (the
McMaster Unbiased Galaxy Simulations 2), we were able to demonstrate a critical
mass at which SN feedback breaks down as a regulator of gas accretion and star
formation.  Galaxies that exceed this mass, $(\sim 10^{12}\;\Msun)$, will produce
more stars than real galaxies, and produce much of these stars in a dense
stellar bulge.  All of this arises due to a fundamental relation between the
mass loading of superbubble driven winds and the mass of the galaxy (either its
halo or its disc).  When the escape velocity of the disc exceeds the sound speed
of superbubble-heated gas (which has a typical mass loading of $\eta=10$), only
outflows which have entrained less material are able to escape the galaxy,
leading to decreasing efficiency in ejecting material, and a shutdown of
SN regulation.  The fact that this shutdown occurs exactly where powerful AGN
are observed, and that it results in a vigorous transport of gas to the nucleus
of the galaxy make this result strong evidence that this shutdown acts as a kind
of ``hand-off'' between SN and AGN feedback.

@@

\section{The Impact and Context of these Results}
Developing a versatile, accurate, resolution insensitve model for feedback has
been a challenge in galaxy simulations for decades \citep{Katz1992}.  While a
number of recent models have been developed that are able to produce galaxies
which match some observables, all of these models have relied on purely
numerical features to enhance the effectiveness of feedback and counter the
lossues due to limited resolution.  The \citet{Keller2014} model presented in Chapter 2 is
the first model of its kind that uses a first-principles approach to prevent
overcooling.  Beyond merely providing ``sufficient'' feedback, the superbubble model also
incorporates physics that previously have been omitted.  Thermal evaporation is
a key process for mixing cold ISM with hot feedback ejecta.  Prior to
\citet{Keller2014}, this process was completely ignored, and the local
mass-loading of feedback was set purely as a numerical parameter.
\citet{Rosdahl2016} illustrated this clearly, in a recent comparison project.
This paper implemented 5 popular feedback algorithms (simple thermal dumps; a
delayed cooling model similar to \citet{Agertz2013}; a kinetic model similar to
\citet{DallaVecchia2008}; a stochastic thermal model based on
\citet{DallaVecchia2012}; and a hybrid model from \citet{Kimm2015}) in the {\sc
RAMSES} code.  This allowed for a controlled test with isolated dwarf and Milky
Way analog galaxies. Each of these models, with ``fiducial'' parameter choices,
produced star formation rates that varied by nearly an order of magnitude in the
\citet{Kennicutt1998} star formation relation.  On top of that, the galaxies
showed marked morphological differences and average wind mass loadings that
varied by more than 4 orders of magnitude.  As we showed in \citet{Keller2015},
these winds are critical to the formation of galaxies like the Milky Way.  
In addition to the inter-model variation, \citet{Rosdahl2016} also found that the
numerical free parameters for each model had a vast impact on the resulting
galaxy's star formation rate, morphology, and outflow properties.  By building a
more conservative, physically motivated model where the local mass loading of
supernovae feedback is set by thermal evaporation, rather than numerically, we
can sidestep many of these issues.

The issue of local mass loading has been explored before in simulation.
\citet{Thacker2000} showed a survey of methods for depositing feedback energy.
This work showed that choosing to deposit feedback energy into single resolution
elements vs. smoothing it over an SPH kernel had a significant impact on whether
that feedback energy could couple to the ISM.  \citet{Thacker2000} advocated the
use of a brief adiabatic period, similar to the delayed cooling model presented
in \citet{Rosdahl2016} to prevent overcooling when feedback energy was smoothed.
A more recent study by \citet{DallaVecchia2012} directly looked at the question
of local mass loading with a model that allowed the temperature of post-feedback
gas to be a single tunable parameter.  This is effectively the same as choosing
the amount of mass that each supernovae couples to (the local mass loading).  They found that lower mass
loadings result in hotter post-feedback gas, with longer cooling times, and
subsequently much more effective supernovae feedback.  The \citet{Keller2014}
superbubble model is the first model to actually incorporate a physical
mechanism for determining this mass loading.  Previous feedback models have been
designed primarily to avoid the overcooling that can occur when this mass
loading is too high: superbubble feedback instead attempts to calculate the {\it
correct} local mass loadings, and allows the feedback-heated gas to cool with
realistic temperatures and densities.  By building a more physically motivated
model for supernovae feedback, we can have better confidence in the results of
simulations testing the effects of this feedback.

As we showed in \citet{Keller2015}, including thermal evaporation in simulations
of a Milky Way like galaxy will drastically change the effectiveness of
SN-driven galactic winds.  Removing gas from the galaxy is the only effective
mechanism for regulating star formation on cosmic timescales.  To prevent the
formation of bulges larger than the ones seen in the local universe, bulge
forming gas (low-angular momentum gas) must be removed from the ISM; because
SN-driven winds are most effective at high redshift, when this material is
mostly accreted, the outflows driven from the galaxy preferentially remove
bulge-forming gas.  A similar result was seen in simulations of dwarf galaxies
by \citet{Governato2010, Brook2011}, but \citet{Keller2015} is the first work to
show that bulgeless disc galaxies similar in mass to the Milky Way can be
produced through the same mechanism, and connect this with the regulation of
star formation.  An important conclusion of this study is that much of the past
work \citet{Stinson2013,Agertz2013,Hopkins2014} showing that SN feedback was
unable regulate star formation without the addition of ``early feedback'' from
radiation pressure, stellar winds, or photoionization was likely underestimating
the effectiveness of SN.  Since many of these studies used simpler, more
numerically-sensitive feedback models that also omitted thermal evaporation,
they were unable to effectively drive the correct amount of mass into hot, high
entropy gas that could leave the galaxy.  This study tells us that the
disc-dominant morphology and low stellar fraction in galaxies like our own all
arise from the same mechanism:  heavily mass loaded, high redshift winds.
